---
title: "R Notebook"
output:
  html_document:
    df_print: paged
  pdf_document: default
---


*1. Upload your dataset (Make sure you are only dealing with the dataset assigned to you).*

## Import libraries
```{r}
library(tidymodels)
```

## Import dataset
```{r}
data <- dataset_2_ILM312_2
head(data)
```

## Perform Exploratory Data Analysis
```{r}
glimpse(data)
```
```{r}
data %>% skimr::skim()
```

*2. Generate your hypothesis for regression analysis. (5 p.)*

*Hypothesis:* 

# H0: There is no linear relationship between SalePrice and the independent variables( "LotArea," "BedroomAbvGr," "GarageArea")

# H1: There is a linear relationship between SalePrice and the independent variables( "LotArea," "BedroomAbvGr," "GarageArea")

3. Check whether your regression assumptions are met (7 p.)

## Check linearity
### LotArea and SalePrice
```{r}
plot(data$LotArea, data$SalePrice)
```
### BedroomAbvGr and SalePrice
```{r}
plot(data$BedroomAbvGr, data$SalePrice)
```
### GarageArea and SalePrice
```{r}
plot(data$GarageArea, data$SalePrice)
```
*Observation:*


*4. Apply regression analysis in R as response variable; SalePrice, explain your model and outcomes generated by R in detail. (10 p.)*
```{r}
model <- lm(SalePrice ~ LotArea + BedroomAbvGr + GarageArea, data = data)
summary(model)
```

*5. State if you reject your null hypothesis or not. (3 p.)*

The F-statistic's p-value is stated as " 2.2e-16," which is significantly lower than the conventional significance level of 0.05. Since there is no linear relationship between "SalePrice" and the independent variables ("LotArea," "BedroomAbvGr," and "GarageArea" we can reject the null hypothesis (H0).

*6. According to the linear regression model that you have generated, predict the sale price of a house if the Lot Area is 9000-meter square, number of bedrooms above the garage is 3 and garage area is 700-meter square.*
```{r}
# Predict the SalePrice
new_data <- data.frame(LotArea = 9000, BedroomAbvGr = 3, GarageArea = 700)
predicted_price <- predict(model, newdata = new_data)
predicted_price

```

